\documentclass{article}
\usepackage{color}
\usepackage[nonumber,index,contents]{cuisine}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{soul}
\usepackage{url}

\setcounter{secnumdepth}{0}

\begin{document}

\RecipeWidths{\textwidth}{0.5\textwidth}{1.0cm}{1.5cm}{1.5cm}{3.0cm}
\renewcommand*{\recipetitlefont}{\large\bfseries}

\tableofcontents

\section{Appetizers \& Hors d'oeuvres}

\begin{recipe}{Bruschetta}{Danielle Worthy --- October 2005}{25 Minutes; 12 Servings}
   \newstep
   Preheat oven to 400\ \0F.

   \Ing{8 Plum Tomatoes}
   \Ing{1/2 Red Onion}
   \Ing{1 Cup Chopped Basil}
   \Ing{Freshly Ground Black Pepper, To Taste}
   Dice the tomatoes and mince the onion.  Combine tomato, onion, and basil in a
   bowl, mixing well.  Season to taste with the pper and set aside.

   \Ing{1 French Baguette}
   Cut the baguette into \fr12 inch thick circles.  Bake the bread until well
   toasted, approximately 5 minutes.  Remote and let cool approximately 3--5
   minutes.

   \Ing{3 Cloves of Garlic}
   Rub the garlic atop the bread until the toast glistens.

   \newstep
   Spoon the tomato mixture onto the toast and serve.

\end{recipe}

\begin{recipe}{Sausage Cheese Puffs}{\href{http://www.bobevans.com/Recipe/17/Sausage-Cheese-Puffs}{Bob Evans Website} --- November 2005}{30 Minutes; 20 Servings}

   \newstep
   Preheat oven to 350\ \0F.

   \Ing{1 Lb Bob Evans Original Recipe Sausage Roll}
   Brown, crumble, and drain sausage.

   \Ing{2 Cups Biscuit Mix}
   \Ing{2\ \fr12 Cups Shredded Sharp Cheddar Cheese}
   \Ing{\fr12 Cup Water}
   \Ing{1 Tsp Baking Powder}
   Combine all ingredients in large bowl until blended.  Shape into 1 inch balls
   and place on baking sheets.

   \newstep
   Bake about 20-25 minutes or until golden brown.

   \freeform
   Serve warm, refrigerate leftovers.

\end{recipe}

\section{Breads \& Doughs}

\begin{recipe}{Banana Bread}{\href{http://www.cookingforengineers.com/recipe/108/Banana-Nut-Bread}{CookingForEngineers.com} --- March 2006}{90 Minutes; 6 Servings}

   \newstep
   Preheat oven to 350\ \0F.

   \Ing{1 \fr13 Cups Flour}
   \Ing{\fr12 Tsp Baking Soda}
   \Ing{\fr14 Tsp Baking Powder}
   \Ing{\fr13 Cup Sugar}
   \Ing{\fr13 Cup Light Brown Sugar}
   \Ing{\fr12 Tsp Salt}
   Combine all dry ingredients.

   \Ing{2 (Overly) Ripe Bananas}
   \Ing{6 Tbsp Melted Butter}
   \Ing{1 Tsp Vanilla Extract}
   \Ing{2 Large Eggs}
   Mash the bananas, melted butter, and vanilla extract together.  Lightly beat
   in the eggs.  Mash the banana mixture with the eggs until smooth and well
   blended.

   \Ing{\fr12 Cup Chopped Walnuts}
   Pour the banana mixture with into the dry ingredients and add the walnuts.
   Fold the mixture together until no more white flour is uncovered.

   \Ing{1 Tsp Butter (or Apple Sauce)}
   Smear butter (or apple sauce) into the baking pan and fill with the batter.

   \newstep
   Bake for 60 Minutes at 350\ \0F.  Cool for 10 minutes and then remove the
   loaf from the pan.

   \freeform
   \emph{Note:} One can substitute cinnamon apple sauce for the butter.  Also,
   one can add \fr13 cup of cinnamon chips to the walnuts for \fr12-1 cup of
   cinnamon chips instead of the walnuts.

\end{recipe}

\begin{recipe}{New York Style Pizza Dough}{Robbie's Recipes --- December 2005}{2 \fr12 Hours; 8 Servings}

   \Ing{1 \fr12 Cups 110\ \0F Water}
   \Ing{2 \fr12 Tsp Granulated Sugar}
   \Ing{2 \fr12 Tsp Salt}
   Dissolve sugar and salt in the water in a large mixing bowl.

   \Ing{1 Tbsp Olive Oil}
   \Ing{4 \fr12 Cups All-Purpose Flour}
   Add oil and flour to bowl and stir with a heavy spoon for one minute.

   \Ing{\fr12 Tsp Active Dry Yeast}
   Turn dough out onto a lightly floured surface and press into a circle.
   Sprinkle the yeast evenly over dough and knead for 12 minutes.

   \newstep
   Divide dough into two equally sized portions for pizza.  Place dough balls in
   a bowl, cover with plastic wrap, and allow to rise for 1 \fr12 hours in a
   warm location.

   \newstep
   Preheat a pizza stone in a 500\ \0F oven for one hour.

   \newstep
   After the dough has risen, place a dough ball on a lightly floured surface
   and sprinkle a light coating of flour on top.  Working from the edges to the
   center, press dough into a 12 inch circle.

   \Ing{\fr12 Cup Cornmeal}
   Coat a large board with cornmeal and place the dough onto the cornmeal.  Put
   on the toppings and transfer everyting to the pizza stone.  Bake in a 500\
   \0F oven for 20-25 minutes, until the crust is golden.

\end{recipe}

\section{Sauces \& Accompaniments}

\begin{recipe}{``Cajun'' Salsa}{Blake Rice --- August 2005}{15 Minutes; 6 Servings}

   \Ing{28 Oz Hunt's \emph{Diced} Tomatoes}
   \Ing{\fr14 Cup Green Onions}
   \Ing{\fr14 Cup Jalapeno}
   \Ing{\fr14 Cup Cilantro}
   \Ing{\fr12 Lime, Juiced}
   Blend all ingredients to desired thickness.

   \freeform
   \emph{Note}: From Blake, ``I find it works best to put half the tomatoes, the
   green onions, and cilantro in first and blend. Then add the rest of the
   tomatoes, the jalapenos, and the lime juice and blend again. Also, drain the
   tomato juice and don't add jalapeno juice to keep it from becoming watered
   down.''

\end{recipe}

\begin{recipe}{Chimichurri Sauce}{munchies.vice.com --- June 2016}{5 Minutes; 20 Servings}

   \Ing{1 Qt Parsley, Chopped}
   \Ing{\fr 12 Cup Garlic, Chopped}
   \Ing{1 Tsp Red Chili Flakes}
   \Ing{2 Tsp Dried Oregano}
   \Ing{1 Tbsp Red Wine Vinegar}
   \Ing{1 Tbsp Salt}
   \Ing{2 Cups Canola Oil}
   \Ing{2 Cups Olive Oil}
   Mix in large bowl; serve over meat at room temperature.

\end{recipe}

\begin{recipe}{Garlic Yogurt}{Random Redditor --- November 2015}{15 Minutes; 6 Servings}

   \Ing{2 Cloves Garlic, Minced}
   \Ing{200 g Greek Yogurt}
   \Ing{1 Pinch Salt}
   \Ing{\fr14 Tsp Dill}
   Mix.

\end{recipe}

\begin{recipe}{Kitchen Pepper}{munchies.vice.com --- June 2016}{5 Minutes}

   \Ing{1 Tbsp Coarsely Ground Black Pepper}
   \Ing{1 Tbsp Kosher Salt}
   \Ing{\fr12 Tbsp Ground Cardamom}
   \Ing{1 Tsp Ground Allspice}
   \Ing{1 Tsp Ground Cinnamon}
   \Ing{1 Tsp Ground Cloves}
   \Ing{1 Tsp Ground Ginger}
   \Ing{1 Tsp Ground Mace}
   \Ing{1 Tsp Ground Nutmeg}
   \Ing{1 Tsp Ground White Pepper}
   \Ing{1 Tsp Red Pepper Flakes}
   Combine in medium bowl; mix well.  Store in dry, cool, place until needed.
   Use sparingly.

\end{recipe}

\begin{recipe}{Spicy Cherry}{Better Homes \& Gardens --- March 1964}{30 Minutes; 12 Servings}

   \Ing{\fr34 Cup Sugar}
   \Ing{1 Dash Salt}
   \Ing{2 Tbsp Cornstarch}
   Combine sugar, salt, and cornstarch.

   \Ing{\fr34 Orange Juice}
   \Ing{1 Tbsp Lemon Juice}
   Stir in orange and lemon juice.

   \Ing{1 Can (14.5 Oz) Pitted Tart Red Cherries (Water Packed)}
   \Ing{\fr12 Tsp Whole Cloves}
   \Ing{1 Inch Cinnamon Stick}
   \Ing{\fr14 Red Food Coloring}
   Over medium heat, add undrained cherries, spices, and food coloring.  Cook,
   stirring constantly until boiling.  Boil two minutes while stirring.  Remove
   from heat, stirring 5 more minutes.

   \freeform
   Remove cinnamon stick and cloves.  Serve warm.

\end{recipe}

\section{Side Dishes}

\begin{recipe}{Macaroni Salad}{Julie Kulesza --- May 2006}{30 Minutes; 8 Servings}

   \Ing{2 Cups Elbow Mararoni, Uncooked}
   Cook pasta as directed on package, drain, chill in cold water, drain again.

   \Ing{\fr12 Cup Onion, Chopped}
   \Ing{\fr12 Cup Celery, Chopped}
   \Ing{\fr12 Cup Green Pepper, Chopped}
   \Ing{\fr12 Cup Radishes, Chopped}
   Mix macaroni with chopped vegetables.

   \Ing{\fr12 -- \fr34 Cup Miracle Whip}
   \Ing{\fr14 -- \fr12 Cup Sour Cream}
   Mix macaroni/vegetables with Miracle Whip and sour cream.

   \Ing{1 Can Dark Red Kidney Beans}
   Drain and rinse beans.  Mix into salad.

   \newstep
   Keep chilled in refrigerator until serving.

\end{recipe}

\begin{recipe}{Potato Salad}{munchies.vice.com --- June 2016}{30 Minutes; 8 Servings}

   \Ing{3 Lbs Yukon gold potatoes}
   Peel and cut potatoes into 1-inch pieces. Place potatoes in a medium saucepan
   and cover them with water. Season with salt and bring to a boil. Cook until
   just tender, about 12 minutes, and drain. Rinse under cold running water
   until cool.

   \Ing{8 Oz Dill Pickles, Cut into \fr14-inch Pieces}
   \Ing{8 Oz Mayonaise}
   \Ing{2 Tbsp Dijon Mustard}
   \Ing{6 Hard-boiled Eggs, Peeled and Diced}
   \Ing{4 Ribs Celary, Diced}
   \Ing{\fr12 Red Onion, Diced}
   Transfer the potatoes to a large bowl with the remaining ingredients and toss
   to combine. Season with salt and pepper. Chill until served.

\end{recipe}

\begin{recipe}{Power Potatoes}{munchies.vice.com --- June 2016}{90 Minutes; 6--12 Servings}

   \newstep
   Preheat oven to 450\ \0F.

   \Ing{6 Large Idaho Potatoes}
   Using a fork, poke holes randomly in the potatoes. Place the potatoes on a
   baking sheet and bake until tender, about 1 hour. 

   \Ing{\fr12 Lb Pancetta, Cubed to \fr14 inch thick lardons}
   \Ing{\fr12 Lb Bacon, Cubed to \fr14 inch thick lardons} 
   In a large skillet, cook the pancetta and bacon over medium-low heat,
   stirring occasionally, until golden, about 20 minutes. Strain through a
   fine-mesh sieve set over a bowl.

   \Ing{2 Heads Broccoli}
   Using your knife, shave off the florets from the broccoli heads into 1/2-inch
   pieces and set aside in a bowl. Cut the broccoli stems into 1/4-inch pieces.
   In a medium saucepan filled with boiling salted water, cook the stems until
   slightly soft but still crunchy, about 1 to 2 minutes. Drain and transfer to
   an ice bath until cold to stop the cooking. Drain the stems again and pat dry
   using paper towels. 
 
   \newstep 
   Remove the potatoes and cool slightly, then cut in half lengthwise and scoop
   out all of the insides with a spoon into a medium bowl, leaving \fr14-inch of
   the outer layer of flesh and skin behind; transfer empty potato halves to a
   baking sheet. 

   \newstep
   Reduce oven to 350\ \0F.

   \Ing{\fr12 Cup Marscapone}
   \Ing{16 Tbsp Butter, Cubed}
   Add marscapone, butter, pancetta, and bacon mixture to scooped potato and mix
   with salt and pepper to taste until malleable.

   \Ing{1 Lb Bocconcini}
   \Ing{1 Cup Grated Cheddar Cheese}
   \Ing{1 Bunch Scallions, Sliced, Greens \& Whites Separated}
   Add the brocolli stems to the potato filling, along with the bocconcini,
   cheddar cheese, and the scallion whites and mix until combined, seasoning
   with salt and pepper. 

   \newstep
   Divide mixture between potato skins. Bake until warmed through, about 20
   minutes longer.

   \Ing{8 Tbsp Butter, Cubed}
   \Ing{2 Tbsp Water}
   Meanwhile in a small saucepan over medium-high heat, melt 8 tablespoons of
   butter with 2 tablespoons of water. Add the reserved broccoli tops and
   scallion greens and cook until bright green, about 2 to 3 minutes. Season
   with salt and pepper and divide among the tops of the potatoes. Keep potatoes
   warm until served.

\end{recipe}

\section{Entrees}

\begin{recipe}{Baked Ziti}{kraftfoods.com --- May 2006}{1 Hour; 8 Servings}

   \newstep
   Preheat oven to 350\ \0F.

   \Ing{16 Oz Ziti Pasta}
   Cook pasta as directed on package; drain.

   \Ing{26 Oz Spaghetti Sauce}
   \Ing{15 Oz Ricotta Cheese}
   \Ing{\fr12 Cup Water}
   \Ing{2 Cups Shredded Mozzarella Cheese}
   \Ing{\fr14 Cup Grated Parmasan Cheese}
   Mix sauce, cheese, and water in large bowl.  Add pasta and \fr12 cup
   Mozzarella cheese; mix lightly.  Spoon into 13\X9-inch baking dish sprayed
   with cooking spray.  Top with remaining Mozzarella cheese and the Parmasan
   cheese.  \emph{Optional}: sprinkle with parsely and oregano to taste.  Cover.

   \newstep
   Bake 30 minutes. Uncover.  Bake an additional 10 minutes.

\end{recipe}

\begin{recipe}{Falafel}{Food Wishes --- November 2015}{0.5 Hours; 4 Servings}

   \Ing{1 Cup Dried Garbanzo Beans}
   Let soak 12-24 hours, completely submerged throughout, in cold water.

   \Ing{\fr12 Onion, Diced}
   \Ing{4 Cloves Garlic, Minced}
   \Ing{\fr12 Cup Italian Parsley, Chopped}
   \Ing{1 Tsp Salt}
   \Ing{1 Tsp Ground Black Pepper}
   \Ing{1 Tsp Cumin}
   \Ing{\fr12 Tsp Ground Coriander}
   \Ing{\fr18 Tsp Cayenne Pepper}
   \Ing{\fr14 Tsp Baking Soda}
   \Ing{1 Tbsp Flour}
   \Ing{2 Tsp Lemon Juice}
   Pulse in food processor until bits are about \fr{1}{16}$^{\prime\prime}$,
   periodically scraping down.

   \newstep
   Shape mixture into balls or patties, approximately 1$^{\prime\prime}$
   diameter. 

   \newstep
   Fry at 350\ \0F for about 5 minutes or until browned and crispy.
   Alternatively, bake at 375\ \0F for 13 minutes, flip, and bake an additional
   13 minutes.

\end{recipe}

\begin{recipe}{Cheeto Macaroni \& Cheese}{munchies.vice.com --- June 2016}{1 Hour; 8 Servings}

   \newstep
   Preheat oven to 400\ \0F.

   \Ing{1 Qt Milk}
   \Ing{2 Lbs American Cheese, Cubed}
   In a large pot over medium heat, add milk. Bring to a simmer. Add cubed
   American cheese little by little, stirring with a spatula until you achieve a
   velvety cheese sauce.

   \Ing{16 Oz Pasta}
   In a separate large pot, add salt to water and boil. Add macaroni, stirring
   every once in a while to make sure they don’t clump together. Do not
   overcook.

   \newstep
   Drain the pasta, add back into the pot. Add cheese sauce until the pasta is
   covered but not soupy. Add cheesy macaroni to the casserole dish.

   \Ing{1 Large Bag Cheetos}
   Smash all the Cheetos up and sprinkle evenly, covering every inch of the
   macaroni.    

   \newstep
   Bake 20--25 minutes or until golden brown.  Let rest 5 minutes before
   serving.

\end{recipe}

\begin{recipe}{Green Macaroni \& Cheese}{munchies.vice.com --- June 2016}{1 Hour; 8 Servings}

   \newstep
   Preheat oven to broil.

   \Ing{10 Oz Baby Spinach}
   \Ing{1 Cup Parsley}
   \Ing{1 Cup Basil}
   \Ing{1 Cup Grated Parmesan Cheese}
   \Ing{1 Clove Garlic}
   Combine in food processor and puree until chunky.

   \Ing{\fr12 Cup Milk}
   Add to food processor mixture and puree until smooth.

   \Ing{4 Tbsp Unsalted Butter}
   \Ing{\fr13 Cup All-purpose Flour}
   \Ing{3 Cups Milk}
   \Ing{6 Oz Grated Sharp White Cheddar Cheese}
   Melt butter in 6-qt. saucepan over medium-high heat; add flour and cook 2
   minutes. Add milk and cook, stirring occasionally, until thick (8--10
   minutes).  Stir in cheese, salt and peppar to taste, and cook until cheese is
   melted.

   \Ing{16 Oz Pasta}
   Cook pasta as directed on package; drain.  Transfer to cheese sauce along
   with spinach and herb blend and stir well to coat. 

   \Ing{6 Oz Grated Sharp White Cheddar Cheese}
   Spread pasta mixture in $9\times13$-inch baking dish and top with
   cheese.  Broil until golden brown and bubbly, 5--7 minutes.  Let cool for 10
   minutes before serving.

\end{recipe}

\begin{recipe}{Southern Macaroni \& Cheese}{Great Southern Classics --- October 2014}{1.5 Hours; 8 Servings}

   \newstep
   Preheat oven to 350\ \0F.

   \Ing{16 Oz Pasta}
   Cook pasta as directed on package; drain.

   \Ing{1 Stick Butter}
   \Ing{\fr12 Cup All-Purpose Flour}
   Heat butter of medium-high heat.  Add flour, stirring to combine.  Cook,
   stirring frequently, until mixture is light brown, approximately 15 minutes.

   \Ing{\fr23 Cup Yellow Onion, Minced}
   Add onion to mixture and continue cooking, stirring frequently, until onion
   is tender.

   \Ing{4 Cups Whole Milk}
   Add milk to mixture, stirring frequently, until mixture begins to thicken,
   approximately 8 minutes.

   \Ing{4 Cups Sharp White Cheddar Cheese, Shredded}
   \Ing{1 \fr34 Cups Smoked Mozzarella Cheese, Shredded}
   \Ing{1 Pound Bacon, Cooked \& Crumbled}
   \Ing{3 Tbsp Whole Grain Mustard \emph{or} 1 Tbsp Dry Mustard}
   \Ing{2 Tbsp Fresh Parsley, Chopped}
   \Ing{\fr12 Tsp Black Pepper, Ground}
   \Ing{\fr12 Tsp Red Pepper, Ground}

   Add cheese, bacon, mustard, parsley, black \& red pepper, stirring until
   cheese is melted.  Add pasta and stir until well combined.

   \Ing{\fr12 Cup Sharp White Cheddar Cheese, Shredded}
   \Ing{\fr34 Cup Sharp Mozzarella Cheese, Shredded}
   Pour mixture into 13\X9 baking dish, top with cheese.

   \newstep
   Bake 20--25 minutes.

   \freeform
   \emph{Note}: The bacon makes this \emph{really} salty.  It is suggested to
   cut the salt anywhere else possible to keep a good balance.
   \newline\newline
   \emph{Note}: At the step where the bacon is added, other inclusions can be
   made such as broccoli florets.

\end{recipe}

\begin{recipe}{Prime Rib}{munchies.vice.com --- June 2016}{5 Hours; 20 Servings}

   \Ing{15 Lb Bone-in Prime Rib Eye} 
   Tie evenly with butcher's twine. Rub entire prime rib with generous amount of
   salt and pepper. Let rest in fridge uncovered for 10 hours or overnight.
   Take out of fridge two hours before cooking and allow to come to room temp.

   \newstep
   Preheat oven to 275\ \0F.  Cook for 3--4 hours, or until the internal
   temperature reaches 110\ \0F for rare or 120\ \0F for medium rare.

   \newstep 
   Tent with foil and let rest 30--45 minutes before serving.  Remove twine and
   slice off ribs along the bone so you remove it in one rack. Slice thin and
   serve.

\end{recipe}

\begin{recipe}{Ribeye Steaks}{munchies.vice.com --- June 2016}{30 Minutes; 4 Servings}

   \Ing{2 (1 \fr12-inch thick) boneless rib-eye steaks (about 1 \fr14 Lbs total)}
   \Ing{2 Tbsp Canola Oil}
   Season the steaks all over with salt. Working in batches, heat oil in a large
   cast-iron skillet over high heat until the oil just begins to smoke. Add 2
   steaks and cook, flipping once, until well browned on both sides, about 6
   minutes.

   \Ing{4 Tbsp Butter, Cubed}
   \Ing{4 Cloves Garlic}
   \Ing{\fr12 Bunch Thyme}
   Add butter, garlic, thyme to steak pan, cook, basting the steaks with the
   butter, until medium-rare, about 2 to 3 more minutes.

   \Ing{2 (1 \fr12-inch thick) boneless rib-eye steaks (about 1 \fr14 Lbs total)}
   \Ing{4 Cloves Garlic}
   \Ing{\fr12 Bunch Thyme}
   Repeat above steps for other two steaks (do not need to add more oil or
   butter).

   \Ing{8 Tbsp Butter, Cubed}
   \Ing{4 Cloves Garlic}
   \Ing{\fr1 Bunch Thyme}
   In a small saucepan, melt butter with garlic and thyme. Cook until the butter
   is well flavored, about 3 to 4 minutes.

   \newstep
   Serve by carving steaks and spooning butter garlic sauce over them with salt
   and pepper.

\end{recipe}

\begin{recipe}{Slow Cooker Ribs}{AllRecipes.com --- November 2015}{6.5 Hours; 6 Servings}

   \Ing{3 Lbs Baby Back Ribs, Trimmed}
   \Ing{\fr12 Onion, Sliced}
   \Ing{1 Clove Garlic, Minced}
   \Ing{\fr12 Cup Water or Beer}
   \Ing{Salt \& Pepper, To Taste}
   Pour water/beer in slow cooker.  Season ribs with salt and pepper.  Layer the
   ribs into the slow cooker.  Top the ribs with the onion and garlic.  Cook on
   high for 3 hours (or low for 6 hours).

   \newstep
   Preheat oven to 375\ \0F.

   \Ing{18 Oz Barbeque Sauce}
   Remove ribs from slow cooker, discard onion and garlic.  Coat ribs with
   barbeque sauce and transfer to baking sheet.  Bake until sauce carmelizes and
   sticks to meat, 10--15 minutes.

\end{recipe}

\begin{recipe}{Two Bear Chili}{Mark Cleaver --- November 2006}{4.5 Hours; 12 Servings}

   \Ing{1 Lb Ground Meat}
   \Ing{Soy or Teriyaki, To Taste}
   Brown and crumble meat, marinated in soy or teriyaki sauce.

   \Ing{1 Can Dark Red Kidney Beans}
   \Ing{1 Can Garbonzo Beans}
   \Ing{2 Cans Pinto Beans}
   \Ing{1 Can Hot Chili Beans}
   \Ing{1 Can Medium Chili Beans}
   \Ing{1 Can Butter Beans}
   Open beans, drain, and rinse.

   \Ing{1 Can of Crushed Tomatoes, Large}
   \Ing{1 Can of Tomato Sauce, Small}
   \Ing{2 Jalapenos, Minced}
   \Ing{1 Pint Honey}
   \Ing{1 Onion, Diced}
   \Ing{1 Packet McCormick Chili Seasoning}
   Combine all ingredients (including meat and beans) in a six quart crock pot.
   Cook for four hours on low temperature, stirring periodically.

   \freeform
   \emph{Original Notes from Mark}:
   \newline\newline
   I have been asked many times for my Chili recipe but, have kept the secrete
   of this old formula hidden for fear of driving the coast of can beans ski
   high.
   \newline\newline
   Recipe is for five quart crock pot.
   \newline\newline
   Open six ot eight cans of assorted beans.  Drain and rinse.  For maximum
   flagilince do not drain beans.
   \newline\newline
   Add one large can of crushed tomatoes.  If whole tomatoes are used,
   \newline\newline
   a, place them under vehicle tires,
   \newline\newline
   b, run over them repeatedly until they are the consistency of theones you
   could have gotten out of a can
   \newline\newline
   c, scrape off road or dump can into large crock pot.
   \newline\newline
   Grill one pound of ground meat, marinated in soy or teriyaki.  Use ground
   sirloin for good taste, ground round for great taste, or use the really cheep
   fatty shit for the most fabulas tasting stuff your goanna eat.
   \newline\newline
   Add to pot.  Grease and all.  Its chili?
   \newline\newline
   Dice very small, two Jahlo peonies, add to pot.  For more spice, add a
   smidgeon of fresh ground habanera pepper.
   \newline\newline
   Sniff pepper to make sure it is fresh.
   \newline\newline
   Add one pint of honey.  If it is too spicy just add more honey.  It won't
   make it any less hot but it makes it go down easier.
   \newline\newline
   Dice one onion add to pot.
   \newline\newline
   Let it gestate for three hours on low temperature.
   \newline\newline
   Take and serve to buddies at card game.  Don't forget to bring beer!
   \newline\newline
   If you put cheese on it you are queer.

\end{recipe}

\begin{recipe}{Miso Ramen}{Jaden Hair --- April 2011}{25 Minutes; 4 Servings}

    \Ing{4 Uncracked Eggs}
    Place eggs in a medium pot and fill with water to cover by 1 inch. Bring to
    boil, turn heat off, and let sit for 10 minutes. Remove each egg with
    slotted spoon, peel under cold running water, and slice in half. 

    \Ing{10 Oz (285 g) Dried Ramen Noodles}
    Bring the same pot of water to a boil. Add ramen noodles and cook according
    to package instruction (Typically 3 minutes). Drain and rinse with cold
    water to stop cooking.

    \Ing{10 Oz (285 g) Cooked Ramen Noodles}
    \Ing{\fr12 Cup (200 g) Fresh or Canned Bamboo Shoots, Sliced}
    \Ing{\fr12 Cup (170 g) Fresh or Canned Corn Kernels, Drained}
    \Ing{\fr13 Cup (80 g) Defrosted Frozen or Fresh Spinach}
    Divide the noodles, hardboiled eggs, bamboo shoots, corn, and spinach among
    4 large serving bowls.

    \Ing{8 Cups (2 Liters) Pork or Vegetable Broth}
    \Ing{2 Teaspoons Instant Dashi Granules}
    \Ing{1 Tablespoon Soy Sauce or to Taste }
    In a large pot, add broth, instant dashi, and soy sauce. Bring to a boil
    over high heat. Remove from heat.

    \Ing{4 Tablespoons Fresh Miso Paste }
    Stir in the miso. Taste soup and add additional 1 to 2 tablespoons if
    wanted. Ladle soup into each bowl.

    \Ing{1 Cup (100 g) Fresh Bean Sprouts}
    \Ing{1 Stalk Green Onion (Scallions), Finely Chopped}
    \Ing{4 Teaspoons Chili Oil (Optional) }
    Top each bowl with fresh bean sprouts, green onions, and a drizzle of chili
    oil, if desired.

\end{recipe}

\begin{recipe}{Chicken Tinola}{Allrecipes.com --- October 2015}{55 Minutes; 4 Servings}

    \Ing{1 Tablespoon Cooking Oil}
    \Ing{1 Onion, Chopped}
    \Ing{2 Cloves Garlic, Minced}
    Heat the oil in a large pot over medium heat. Cook and stir the onion and
    garlic in the hot oil until fragrant.

    \Ing{1 (1 \fr12 Inch) Piece Fresh Ginger, Peeled and Thinly Sliced}
    \Ing{1 Tablespoon Fish Sauce}
    \Ing{3 Pounds Chicken Legs and Thighs, Rinsed and Patted Dry}
    Quickly stir the ginger and fish sauce into the pot before adding the
    chicken. Cook together for 5 minutes.

    \Ing{2 (14 Ounce) Cans Chicken Broth}
    Pour the chicken broth over the mixture and cook another 5 minutes.

    \Ing{1 Chayote Squash, Peeled and Cut Into Bite-Sized Pieces}
    Add the chayote to the pot and simmer for 10 minutes.

    \Ing{Salt and Pepper, to Taste}
    \Ing{1 Head Bok Choy, Chopped}
    \Ing{\fr12 Pound Spinach}
    Season with salt and pepper. Add the bok choy and spinach. Cook until the
    spinach is just wilted, about 1 to 2 minutes.

    \newstep
    Serve hot.

    \freeform
    \emph{Note}: From Aaron, ``I ate this a lot growing up in the Philippines. I
    haven't bothered to contact the old cook and ask what ingredients she used,
    but this one I found online tastes the same''


\end{recipe}

\begin{recipe}{Masa'aa (Eggplant Dish)}{\href{http://www.geniuskitchen.com/recipe/egyptian-eggplant-dish-masaaa-419171}{GeniusKitchen.com} --- July 2018}{90 Minutes; 5 Servings} 

  \Ing{Oil, For Frying}
  \Ing{1 Large Eggplant, \fr12" Slices}
  Fry the eggplant slices in oil until golden, set aside on paper towels to
  drain, and lightly salt.

  \Ing{4 Large Red Potatoes, Cubed}
  Fry potato cubes until golden brown, set aside on paper towels to drain, and
  lightly salt.

  \Ing{1 Green Bell Pepper, Sliced}
  Fry pepper slices in oil until tender, set aside.

  \Ing{1 Large Red Onion, Thinly Sliced}
  \Ing{2 Garlic Cloves, Chopped}
  In a pan, saute the onion until soft. Add garlic and saute 1-2 min more.

  \Ing{1 Tsp Cumin}
  \Ing{1 Tsp Coriander}
  \Ing{\fr12 Tsp Ground Pepper}
  \Ing{1 Tsb Ground Mustard}
  \Ing{Salt, To Taste}
  Add the spices over onions and garlic in pan and stir.

  \Ing{15oz Can Tomato Sauce}
  \Ing{15oz Can Chickpeas, Rinsed and Drained}
  Add in the eggplant, potatoes, bell pepper, and tomato sauce. Mix well. Cook
  just long enough to heat through. Add chickpeas.

  \freeform
  \emph{Note}: All the frying can be done in the same pan or wok. There is no
  need to change oil between vegetables. The chopping required is time
  consuming but well worth it since this dish seems to last over a week in the
  fridge.

\end{recipe}

\section{Desserts}

\begin{recipe}{Blonde Brownies}{Toll House Morsel Package --- November 2005}{40 Minutes; 36 Servings}

   \newstep
   Preheat oven to 350\ \0F. Grease 15\X10 inch jelly roll pan.

   \Ing{2\ \fr14 Cups All-Purpose Flour}
   \Ing{2\ \fr12 Tsp Baking Powder}
   \Ing{\fr12 Tsp Salt}
   Combine flour, baking powder, and salt in a small bowl.

   \Ing{1\ \fr34 Cups Packed Brown Sugar}
   \Ing{\fr34 Cup (1\ \fr12 Sticks Butter, Softened}
   Beat sugar and butter in large mixer bowl until creamy.

   \Ing{3 Large Eggs}
   \Ing{1 Tsp Vanilla Extract}
   Beat in eggs and vanilla extract; gradually beat in flour mixture.

   \Ing{2 Cups (12 Oz) Chocolate Chips}
   Stir in morsels.

   \newstep
   Spread in jelly roll pan.  Bake for 20 to 25 minutes or until top is golden
   brown.  Cool in pan on wire rack.

\end{recipe}

\begin{recipe}{Brownies}{Louis Borges --- May 2015}{75 Minutes; 8 Servings}

   \newstep
   Preheat oven to 350\ \0F.

   \Ing{\fr34 Cup Oil}
   \Ing{1\ \fr12 Cups Sugar}
   \Ing{1 \fr12 Tsp Vanilla}
   \Ing{3 Eggs}
   Mix oil, sugar, vanilla.  Add eggs and continue mixing.

   \Ing{\fr34 Cup Flour}
   \Ing{\fr13 Cup + 2 \fr12 Tsp Cocoa}
   \Ing{\fr38 Tsp Baking Powder}
   \Ing{\fr14 Tsp Salt}
   Add flour, cocoa, baking powder, and salt, mixing to combine.

   \newstep
   Bake for 35 minutes, allowing to cool for an additional 30 minutes, before
   serving.

\end{recipe}

\begin{recipe}{Queijadas de Leite}{Louis Borges --- May 2015}{1 Hours; 12 Servings}

   \newstep
   Preheat oven to 350\ \0F.

   \Ing{2 Cups Sugar}
   \Ing{3 Eggs}
   \Ing{1/2 Stick Butter, Melted}
   \Ing{1 Tbsp Vanilla}
   Beat together the sugar, eggs, butter ,and vanilla on medium speed for two
   minutes.

   \Ing{3 Cups Milk}
   \Ing{1 Cup Flour}
   Incorporate milk and flour slowly until well mixed.

   \newstep
   Grease cupcake pans (or use cupcake baking papers) and add a little flour.
   Pour in mixture.  Bake for 45 minutes.

\end{recipe}

\begin{recipe}{Saltine Toffee Candy}{Julie Kulesza --- December 2006}{30 Minutes; 40 Servings}

   \Ing{40 Saltine Crackers}
   Line up the saltines on a jelly roll pan that has been lined with foil and
   sprayed with Pam.  There should be five rows by eight columns.

   \Ing{1 Cup Butter}
   \Ing{1 Cup Light Brown Sugar}
   Melt butter and add light brown sugar.  Stir often and bring to a full
   rolling boil for exactly 3 minutes.

   \newstep
   Pour mixture over saltines and bake in a 400\ \0F oven for five minutes.

   \Ing{12 Oz Semi-Sweet Chocolate Chips}
   Sprinkle the chocolate chips over the entire surface and wait until they are
   almost melted; spread over all the saltines.

   \Ing{1 Cup Nuts of Your Choice (Chopped or Ground)}
   Drop the nuts over the top as evenly as possible. Use the buttered bottom of
   a measuring cup or glass to lightly press into the chocolate.

   \newstep
   Refrigerate for two hours and then break into pieces.  Can be stored in a
   tin.

\end{recipe}

\begin{recipe}{Swedish Chocolate Balls}{\href{http://www.allrecipes.com/recipe/swedish-chocolate-balls-or-coconut-balls/}{AllRecipes.com} --- May 2015}{2 Hours, 20 Minutes; 24 Servings}

   \Ing{1 Cup Butter, Softened}
   \Ing{4 Cups Regular Rolled Oats}
   \Ing{1\ \fr14 Cups White Sugar}
   \Ing{\fr12 Cup Unsweetened Cocoa Powder}
   Mix the oats, sugar, and cocoa together in a bowl. Add the butter, and use your
   hands to mix the ingredients together to make a thick dough.

   \Ing{2 Squares (1 Oz) Unsweetened Baking Chocolate, Melted}
   \Ing{2 Tbsp Strong Coffee}
   \Ing{1 Tsp Vanilla Extract}
   Mix in the coffee, vanilla, and chocolate until thoroughly blended.

   \Ing{\fr13 Cup Coconut Flakes}
   Place the coconut flakes in a small bowl. Pinch off small amounts of dough and
   roll between your hands to make small balls, about 1\ \fr12 inches in diameter.
   Roll the balls in the coconut flakes. Balls should be refrigerated 2 hours to
   become firmer.

   \freeform
   \emph{Note}: The oats can be processed in a food processor to vary the
   texture of the final ball.  However, this will introduce sharp edges onto
   the oats which makes mixing by hand more difficult (i.e., painful).

\end{recipe}

\begin{recipe}{Walnut Fudge}{Mrs. Dodd --- December 2005}{45 Minutes; 16 Servings}

   \Ing{1 \fr12 Cups (3 Sticks) Butter}
   \Ing{6 Cups Sugar}
   \Ing{1 \fr13 Cups Evaporated Milk}
   Mix butter, sugar, and milk in large saucepan.  Over low heat, stir until
   butter melts.

   \newstep
   Bring to a full boil, stirring constantly for five minutes.

   \Ing{24 Oz Semi-Sweet Chocolate Chips}
   \Ing{13 Oz Jar Marshmallow Creme}
   \Ing{2 Tsp Vanilla}
   \Ing{2 Cups Chopped Walnuts (Optional)}
   Remove from heat and add chocolate chips, marshmallow cream, vanilla (and
   nuts).  Stir until melted and mixed.

   \newstep
   Pour into 2, 13\X9-inch pans or 3, 9-inch square pans.  Cool at room
   temperature.

\end{recipe}

%\section{Drinks}

\end{document}
